02_DESeq_characterization

### 2019-12-22 analysis/03_DESeq2_characterization.Rmd
remove old files, working on new lda analysis

```{r allvolcanos, fig.height=6}
background <- png::readPNG("../figures/images/DoveParentsRNAseq_charicons.png")
icons <- ggdraw() +  draw_image(background, scale = 1)
plot_grid(icons, hypothalamus, pituitary, gonads, nrow = 4, rel_heights = c(1,1,1,1.25))
```

>>>>

```{r allvolcanos, fig.height=6}
background <- png::readPNG("../figures/images/DoveParentsRNAseq_charicons.png")
icons <- ggdraw() +  draw_image(background, scale = 1)
plot_grid(icons, hypothalamus, pituitary, gonads, nrow = 4, rel_heights = c(1,1,1,1.25))
